---
title: "Shuai Wang"
subtitle: "Geospatial Data Analytics & City Planning"
format: html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center"
)
```

```{r}
#| column: screen

library(tidyverse)
library(gtrendsR)
library(showtext)
library(ggthemes)
library(cowplot)
library(magick)
library(ggimage)
theme_set(theme_cowplot())

#font_add(family = "BloodyTerror-GOW9Z.ttf", regular = "BloodyTerror-GOW9Z.ttf")
showtext_auto()

#wednesday_search<-gtrendsR::gtrends(
#  keyword= c("Wednesday Addams"),
#  time = "today 1-m"
#)

#wednesday_hits <- wednesday_search$interest_over_time %>% 
 # mutate(date=as.Date(date),
 #        hits = replace_na(as.numeric(hits),0))


```

## Education

#### **University of Pennsylvania**, *Philadelphia, PA (Aug 2023 -- Present)*

**Master of City Planning in Spatial Analytics**

-   Relevant courses: Geospatial Cloud Computing (SQL), Machine Learning in Remote Sensing (Python), Public Policy Analytics (R), Quantitative Analysis Methods (R)

#### **University of Liverpool**, *Liverpool, UK*

**Bachelor of Arts in Urban Planning**

-   Relevant courses: Geospatial Data Science (Python), Urban & Environmental Economics

## Professional Experience

#### **Transport Planning and GIS Intern**, *Liverpool, UK (Jun - Sep 2022)*

**Mott Macdonald**

#### **Urban Planning and Design Intern**, *Suzhou, China (Jul - Aug 2021)*

**Suzhou Planning & Design Research Institute**

## Research Experience

#### **Geospatial Research Assistant**, *Philadelphia, PA (Dec 2023 - Present)*

**Business and Conflict Barometer Initiative, The Wharton School**

#### **Undergraduate Transport Researcher**, *Liverpool, UK (Apr 2022 - Jun 2023)*

**School of Environmental Science, University of Liverpool**

#### **Undergraduate Researcher**, *Suzhou, China (Jun - Sep 2021)*

**Department of Urban Planning, Xi'an Jiaotong-Liverpool University**

## Extracurricular Experience

#### **Content Planning Board Member**, *Philadelphia, PA (Sep 2023 - Present)*

**Wharton Future of Cities Conference**

## Skills & Hobbies

-   Technical skills: R (dplyr, tidyverse, etc.) | Python (pandas, numpy, etc.) | ArcGIS Pro, QGIS | Microsoft Excel | Adobe Illustrator & Photoshop
-   Interests: Amateur baker, world traveling, exploring parks, hiking, photography in new cities

<br>
